Leveraging Diversity to Find Bugs\\ in JavaScript Engines

### 2018-08-16 paper/paper.tex
revised tables

\subsubsection{Results}
Table~\ref{tab:summary-of-results} summarizes our results. It shows,
for each fuzzer and kind of bucket (\ie{}, hi or lo), the total number
of files involved, the number of buckets reported by our
infrastructure, the number of those that we classified as
bug-revealing (positive), and the number of those that we filed a bug
report. The difference between the last two columns corresponds to the
number of duplicates, \ie{}, the cases of bugs already reported in the
corresponding issue tracker. As expected, the hit ratio for the ``hi''
group is higher, indicating that chances of filing a bug report for a
``hi'' warning is higher.

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-of-results}Summary of results.}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{mode} & \multirow{2}{*}{type} & \multirow{2}{*}{\# files} &  \multicolumn{3}{c}{buckets} \\
    \cline{4-6}    
    & & & \multicolumn{1}{c}{\#} & \multicolumn{1}{c}{\# pos.} &
    \multicolumn{1}{c}{\# pos. filed} \\
    \midrule
    %% \multirow{2}{*}{nofuzz} & lo & \nofuzzFilesLO{} &  \nofuzzLOTotal{} & \Fix{.} & 11 (34) \\
    %% & hi & \nofuzzFilesHI{} & \nofuzzHITotal{} & \Fix{.} & \Fix{108 (-)} \\
    \multirow{2}{*}{\radamsa} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
    \multirow{2}{*}{\quickfuzz} & lo & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\
                             & hi & \Fix{.} & \Fix{.} & \Fix{.} & \Fix{.} \\    
    \bottomrule     
  \end{tabular}
\end{table}

>>>>

\subsubsection{Results}
\Mar{revise text...}
\Fix{
Table~\ref{tab:summary-of-results} summarizes our results. It shows,
for each fuzzer and kind of bucket (\ie{}, hi or lo), the total number
of files involved, the number of buckets reported by our
infrastructure, the number of those that we classified as
bug-revealing (positive), and the number of those that we filed a bug
report. The difference between the last two columns corresponds to the
number of duplicates, \ie{}, the cases of bugs already reported in the
corresponding issue tracker. As expected, the hit ratio for the ``hi''
group is higher, indicating that chances of filing a bug report for a
``hi'' warning is higher.}

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-lo}Summary of \lo\ warning reports.}
  \begin{tabular}{crr}
    \toprule
    & \# buckets & avg. \# files per bucket \\
    \midrule
    \radamsa{} & & \\
    \quickfuzz{} & & \\    
    \bottomrule     
  \end{tabular}
\end{table}

\begin{table}[h]
  \centering
  \caption{\label{tab:summary-hi}Number of \hi\ warning
    reports per engine.}
  \begin{tabular}{crrrr}
    \toprule
    fuzzer\textbackslash{}engine & \jsc\ & \veight\ & \chakra & \smonkey \\
    \midrule
    \radamsa{} & & \\
    \quickfuzz{} & & \\    
    \bottomrule     
  \end{tabular}
\end{table}
